Accelerated evolution of convective simulations

### 2018-03-14 tex/bvp_paper.tex
updates to figures, need to finalize text

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

@@

\vspace{5cm}
$\,$\newline
The time- and volume-averaged values of the Nusselt number (Nu), the RMS
Reynolds number (Re), and the mean temperature in AE solutions 
are shown in Fig. \ref{fig:parameter_space_comparison}a-c.
Nu, which quantifies the heat transport in evolved solutions,
is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
Nu is defined as
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
\end{equation}
where the volume average of a quantity, $g$, is shown as $\angles{g}$.
When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
the evolved system is characterized by a specific
value of Nu, as the convective heat transport reaches a temporally stationary state.
At larger values of $S$ in 2D, the convective plumes consistently oscillate
horizontally, leading to variations in Nu over time as the heat transport is alternately
assisted and diminished by these oscillations.
As a result of our choice of no-slip
boundary conditions, the fluid never enters a full domain shearing state 
\cite{goluskin&all2014}, and the
oscillatory nature of the plumes is stable.
The 2D SE simulations exhibit the same horizontally
oscillatory behavior as the AE solutions for the same initial conditions. The
dynamic nature of the plume structures diminishes the
scaling of the heat transport to $\text{Nu} \propto \text{Ra}^{1/5}$,
which is weaker than classic scaling laws \cite{johnston&doering2009, ahlers&all2009}.
Previous studies in 2D convection may have avoided oscillatory plumes by using
bootstrapping techniques as initial conditions for high $S$ runs.

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement.  Vertical lines represent the standard deviation of the measurement,
and quantify natural variation over the
averaging window. Error bars represent the change in the mean value over the averaging window,
such that very large error bars represent solutions which are not fully converged when averaging
begins.
(a) Nu scales as Ra$^{1/5}$; above S$\geq 10^{3+2/3}$,
simulations exhibit oscillating plume structures whose heat transport fluctuates over time.  
(b) Re, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at $z = +1/2$
is shown, and this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
Relative error for measurements of (d) Nu, (e) Re, and (f) $T$ between 
AE solutions and SE solutions are shown.
The greyed area of the plots indicates the region in which only AE runs were
carried out due to computational expense. The run at $S = 10^5$ marked as a
black square is examined in more detail in Figs. \ref{fig:time_trace},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
\label{fig:parameter_space_comparison} }
\end{figure}

In Fig. \ref{fig:parameter_space_comparison}b, we report 
$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measures the degree of
turbulence in the solution, and scales roughly as
$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
the value of Re over time.

Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$.
The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
so this measurements serves as a probe of the temperature jump across the boundary
layers. As a result, we expect this measure to
scaling inversely with Nu in converged solutions
where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
scaling of Nu.

@@

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
at $S = 10^{5}$ are shown.  (a) Evolved horizontally- and time-averaged 
temperature profiles, as a function of height.
(b) Probability Distribution Functions (PDFs) and their integrated
Cumulative Distribution Functions (CDFs)
of point-by-point measurements of the temperature field.
$T$ is sampled every 0.1 time units for 500 total time units,
and was interpolated onto an evenly spaced grid before sampling.
(c) The percentage difference between the mean temperature profiles as a function of height.
The difference between the mean profiles is very small, O(0.5\%).
(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
the AE and SE CDFs, as a function of temperature.
The small
difference in the interior temperature 
results in a large difference between the two temperature CDFs near the values
of the temperature modes.  The spread of temperature around the modes, which includes the 
fluctuations that drive convection, are nearly identical between the two runs.
\label{fig:temp_comparison} }
\end{figure}

The probability distribution functions (PDFs)
of point-by-point temperature measurements are compared for the two runs
in Fig. \ref{fig:temp_comparison}b. To construct these PDFs, 
we interpolate the temperature field
of each of these snapshots onto an evenly spaced grid, determine the
frequency distribution of all measured $T$ values, and then normalize the
distribution such that its integral is unity.  The two PDFs have noticeably
different modes, as is expected from Fig. \ref{fig:temp_comparison}a. 
Over long timescales, the 0.5\% difference between the two profiles would
disappear, as the AE solution evolves to be exactly the SE solution -- this
is evident in the asymmetry of the AE PDF in Fig. \ref{fig:temp_comparison}b and also
the trend of the mean temperature over time in Fig. \ref{fig:temp_comparison}c.

One means of comparing two
PDFs to determine if they are drawn from the same underlying
sample distribution is through the use of a Kolmogorov-Smirnov (KS) \cite{wall&jenkins2012}.
In general, a KS test must be conducted on independent, uncorrelated data, which
poorly describes the point-by-point values of flows in a fluid simulation. Thus,
we cannot directly use a KS test to determine if the two fluid samples are the same,
but we can draw insight from the profile
$\text{KS} = \text{CDF}_{\text{AE}} - \text{CDF}_{\text{SE}},$
where CDF stands for cumulative distribution function, the integral of the PDF.
A traditional Kolmogorov-Smirnov statistic is the maximum of the absolute value of
the KS profile.  We show the KS profile in Fig. \ref{fig:temp_comparison}d, and the
CDFs used to construct it overlay the PDFs in Fig. \ref{fig:temp_comparison}b.
Near the modes of the temperature PDFs, the KS profile has a maximum value of
0.495, which is very large and implies that roughly half of all temperature
measurements in the SE case are greater than those in the AE case.
This difference is significant, and shows that the two PDFs are distinctly different,
but aside from this large value near the modes the KS profile has very small values,
indicating that the temperature fluctuations away from the modes in the two cases are nearly identical.

In addition to comparing the thermodynamic state achieved by the SE and AE methods,
we examine the velocities found in the evolved states.
Shown are the PDFs of 
vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
and the nonlinear vertical convective flux (Fig. \ref{fig:pdf_comparison}c). 
The CDFs of each profile are overplotted, and corresponding KS profiles are
shown in Fig. \ref{fig:pdf_comparison}d-f.  The maximum absolute values of the
KS profiles of vertical velocity, horizontal velocity, and nonlinear vertical convective flux
are 0.00615, 0.0349, and 0.0263, respectively.  
Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
velocity boundary conditions (Eqn. (\ref{eqn:bcs})).
The difference in vertical velocity
and heat transport is negligible, which is unsurprising in light of
the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
The horizontal velocity shows some small deviation between the two simulations, and this
likely relates to the nature of the strength of the horizontally oscillatory motions
as we previously described in the context of suppressed Nu scaling. Thus, while
the temperature profiles are distinctly drawn from different distributions in
Fig. \ref{fig:temp_comparison}b, the profiles are similar enough that they drive
nearly identical nonlinear dynamics.

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{Probability distribution functions (PDFs) of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
at $S = 10^{5}$.  Flows are sampled every 0.1 time units for 500 total time units,
and are first interpolated onto an evenly spaced grid.
The cumulative distribution function (CDF) is overplotted for each PDF. 
(d-f) The KS statistics, or the values of CDF$_{\text{AE}}$ - CDF$_{\text{SE}}$,
are shown for the related distributions, and solid lines indicated positive values
while dashed lines are negative values. Unlike the temperature distributions in
Fig. \ref{fig:temp_comparison}, these distributions, particularly the vertical
velocity and transport, show very good agreement and small values of the KS statistic.
\label{fig:pdf_comparison} }
\end{figure}

@@

\section{Extensions \& Conclusion}
\label{sec:extensions}
In this work we have studied a method of Accelerated Evolution (AE) which can
be employed to achieve rapid thermal convergence of convective simulations.  We compared
this technique to the Standard Evolution (SE) of convection through a thermal diffusion timescale and
showed that AE rapidly obtains solutions whose dynamics are similar to SE solutions.
The AE method is not only valid at low values of $S$, where SE solutions
converge quickly due to the short thermal timescale, but AE is also applicable
at high values of $S$, where SE solutions are intractable.
We have studied
the AE method in both 2D and 3D, but restricted most of our study to 2D flows;
AE depends only on 1D, horizontally averaged profiles of dynamics, and our inclusion of 3D
simulations was merely to demonstrate the broadly useful nature of AE.

@@

Convection in natural systems is often driven by internal heating processes
rather than imposed, fixed boundary conditions. The AE procedure can be straightforwardly
applied to Boussinesq studies of internally heated convection \cite{goluskin2016},
where a constant source term in the energy equation causes 
the vertical flux through the system to increase with height.
These systems can be
studied using exactly the methods that we examined here, but 
multiplying the flux profiles derived
in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux. Studies of
convection in natural system often employ height-dependent conductivities
\cite{brandenburg2016, kapyla&all2017}, leading
to natural flux divergences that act as internal heating terms.
The study
of AE method in the context of simple internal heating simulations will be an important step
towards achieving AE in simulations with astrophysically realistic conductivities.

A further area which could benefit from AE is overshooting convection, in which
studies examine adjacent stable and convecting regions
\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
When the interface between the stable region
and the convecting region is stiff and motions do not cross that interface,
convective motions cannot accelerate the restratification of the stable region.
In fully-convective domains, such as those studied in this work, the thermodynamics evolve
at a more rapid rate than the thermal diffusion time across the domain due to
the help of convective motions.  For example, in Fig. \ref{fig:time_trace}a,
the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
despite the thermal timescale being roughly $10^4$ freefall units. However, in 
studies where there is a stable region which is not mixed by convection, the experimentalist
must either wait through a thermal diffusion time for the region to restratify
or employ other methods \cite{couston&all2017} to study evolved atmospheres.

Studies of stratified, compressible convection have much to gain through
developing and employing AE.
In many studies of stratified convection, the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}. Thus, the
thermal timescale grows with depth in the atmosphere, and
the difficulty of achieving thermal convergence grows as simulators study more highly
stratified domains.
In order to extend AE into this regime, two additional pieces of information must be considered.
First, rather than constructing the profiles in Eqn. (\ref{eqn:bvp_ratios})
with the total flux through the domain, only the superadiabatic portion of
the flux should be considered.
Second, in addition to solving for
hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously evolve the density
profile in a manner which conserves mass.  In a 1D boundary value problem, such as
is solved to achieve AE here, this implies the inclusion of an equation which tracks
the vertically integrated mass, and sets boundary conditions on that mass to ensure
that no mass enters or leaves the domain.

@@

While the use of a single AE BVP solve rapidly advances the convecting state to
one that is closer to the evolved state, we find that repeating this method 
multiple times is the best way to
ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
set $t_{\text{transient}} = 50$, completed an AE BVP solve
with $t_{\text{min}} = 30$ and $P = 0.1$, and then repeated the procedure.
For all 3D runs and 2D runs with $S \in [10^5, 10^6]$,
we did a first AE BVP solve with $t_{\text{transient}} = 20$,
$t_{\text{min}} = 20$, and $P = 1$ in order to quickly reach a near-
converged state and vastly increase our timestep size.  After this first solve, 
we completed two AE BVP solves, with $t_{\text{transient}} = 30$,
$t_{\text{min}} = 30$, 
and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}c).
At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
$P = 1$. For the first solve, we set $t_{\text{transient}} = 20$, and for the
second we set $t_{\text{transient}} = 30$. We used fewer solves at this high
value of $S$ in part to reduce the computational expense of the run, and in
part because a third BVP generally did not greatly alter the solution
(as in Fig. \ref{fig:time_trace}c, arrow 3).

>>>>

\newcommand{\Div}[1]{\ensuremath{\nabla\cdot\left( #1\right)}}
\newcommand{\DivU}{\ensuremath{\nabla\cdot\bm{u}}}
\newcommand{\angles}[1]{\ensuremath{\left\langle #1 \right\rangle}}
\newcommand{\KS}[1]{\ensuremath{\text{KS}(#1)}}
\newcommand{\KSstat}[1]{\ensuremath{\overline{\text{KS}(#1)}}}
\newcommand{\grad}{\ensuremath{\nabla}}
\newcommand{\RB}{Rayleigh-B\'{e}nard }
\newcommand{\stressT}{\ensuremath{\bm{\bar{\bar{\Pi}}}}}
\newcommand{\lilstressT}{\ensuremath{\bm{\bar{\bar{\sigma}}}}}
\newcommand{\nrho}{\ensuremath{n_{\rho}}}
\newcommand{\approptoinn}[2]{\mathrel{\vcenter{
	\offinterlineskip\halign{\hfil$##$\cr
	#1\propto\cr\noalign{\kern2pt}#1\sim\cr\noalign{\kern-2pt}}}}}

@@

\begin{figure}[t!]
\includegraphics[width=\textwidth]{./figs/oscillating_plumes.png}
\caption{. \label{fig:oscillating_plumes} }
\end{figure}

The Nusselt number (Nu) quantifies the efficiency of convective heat transport
and is defined as
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - \mathcal{P}\partial_z T}}{\angles{- \mathcal{P} \partial_z T}},
\end{equation}
where the volume average of a quantity, $\eta$, is shown as $\angles{\eta}$.
When $S < 10^{3+2/3}$ in 2D and for all runs in 3D, 
the evolved system is characterized by a specific
value of Nu, as the convective heat transport reaches a temporally stationary state.
At larger values of $S$ in 2D, the value of Nu varies significantly over time,
as shown by the time traces for $S = 10^5$ (top) and $S = 10^7$ (bottom) for two
AE runs in Fig. \ref{fig:oscillating_plumes}. We find that these systems go between
states in which temperature fluctuations primarily travel in their natural buoyant
direction (as in Ia and IIa, where cold elements are falling and hot elements rise),
and states in which temperature perturbations are entrained in an upflow or downflow
with oppositely signed fluid (as in Ib and IIb, where warm fluid is pulled down by the downflow
lane, and cool fluid is pulled up by the upflow lane).  The fluid from the oppositely
signed plume pushes on the other plume such that the system goes between states in which
the fluid primarily serves to enhance convective transport (Ia and IIa), states in which
there is counterclockwise entrainment (IIa and IIb), then back to enhanced transport states
followed by clockwise entrainment.  This horizontally oscillatory motion that characterizes the
plumes provides, and the resultant time-dependent entrainment, leads to large variations in Nu over time 
As a result of our choice of no-slip
boundary conditions, the fluid never enters a full domain shearing state 
\cite{goluskin&all2014}, and the
oscillatory nature of the plumes is stable.
The 2D SE simulations exhibit the same horizontally
oscillatory behavior as the AE solutions for the same initial conditions. 
This time-dependent behavior or Nu is not seen strongly in our 3D solutions,
likely as a result of the extra degrees of freedom in which rising and falling
fluid elements can expand, reducing entrainment.

The time- and volume-averaged values of the Nusselt number (Nu), the RMS
Reynolds number (Re), and the mean temperature in AE solutions 
are shown in Fig. \ref{fig:parameter_space_comparison}a-c.
Nu, which quantifies the heat transport in evolved solutions,
is shown as a function of Ra and $S$ in Fig. \ref{fig:parameter_space_comparison}a.
The
dynamic nature of the plume structures diminishes the
scaling of the heat transport to $\text{Nu} \propto \text{Ra}^{1/5}$,
which is weaker than classic scaling laws \cite{johnston&doering2009, ahlers&all2009}.
Previous studies in 2D convection may have avoided oscillatory plumes by using
bootstrapping techniques as initial conditions for high $S$ runs.
In Fig. \ref{fig:parameter_space_comparison}b, we report 
$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  This measures the degree of
turbulence in the solution, and scales roughly as
$\text{Re} \propto \text{Ra}^{0.45}$. Each simulation shows little variance in
the value of Re over time.
Fig. \ref{fig:parameter_space_comparison}c shows the scaling of $\angles{T} - T_{\text{top}}$.
The average temperature, $\angles{T}$, is dominated by its value in the isothermal interior,
so this measurements serves as a probe of the temperature jump across the boundary
layers. As a result, we expect this measure to
scale inversely with Nu in converged solutions
where fixed-flux boundary conditions are used \cite{otero&all2002}.  We find here
that $(\angles{T} - T_{\text{top}}) \propto \text{Ra}^{-1/5}$, precisely the inverse
scaling of Nu.

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements of the Nusselt number (Nu), the
RMS Reynolds number (Re), and the mean temperature ($\angles{T}$) for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement and denote 2D (purple circles) and 3D (red stars). 
The run at $S = 10^5$ marked as a
black square is examined in more detail in Figs. \ref{fig:time_trace}, \ref{fig:oscillating_plumes},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
Vertical lines represent the standard deviation of the measurement,
and quantify natural variation over the averaging window. 
(a) Nu scales as Ra$^{1/5}$; above S$\geq 10^{3+2/3}$,
simulations exhibit oscillating plume structures whose heat transport fluctuates over time
as a result of temporally-varying entrainment of wrongly signed temperature perturbations
(see Fig. \ref{fig:oscillating_plumes}).  
(b) Re, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$. (c) The difference between $\angles{T}$ and the value of $T$ at $z = +1/2$
is shown, and this quantity scales as Ra$^{-1/5}$, the inverse of Nu.
Relative error for measurements of (d) Nu, (e) Re, and (f) $T$ between 
AE solutions and SE solutions are shown.
The greyed area of the plots indicates the region in which only AE runs were
carried out due to computational expense. \label{fig:parameter_space_comparison} }
\end{figure}

This is a short paragraph which says 2D and 3D are the same, here.

@@

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
at $S = 10^{5}$ are shown.  (a) Evolved horizontally- and time-averaged 
temperature profiles, as a function of height.
(b) Probability Distribution Functions (PDFs) and their integrated
Cumulative Distribution Functions (CDFs)
of point-by-point measurements of the temperature field.
(c) The percentage difference between the mean temperature profiles as a function of height.
The difference between the mean profiles is very small, O(0.5\%).
(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
the AE and SE CDFs, as a function of temperature.
The small
difference in the interior temperature 
results in a large difference between the two temperature CDFs near the values
of the temperature modes.  The spread of temperature around the modes, which includes the 
fluctuations that drive convection, are nearly identical between the two runs.
\label{fig:temp_comparison} }
\end{figure}

The probability distribution functions (PDFs)
of point-by-point temperature measurements are compared for the two runs
in Fig. \ref{fig:temp_comparison}b. To construct these PDFs, 
we interpolate the temperature field
of each of these snapshots onto an evenly spaced grid, determine the
frequency distribution of all measured $T$ values, and then normalize the
distribution such that its integral is unity.  The two PDFs have noticeably
different modes, as is expected from Fig. \ref{fig:temp_comparison}a. 
Over long timescales, the 0.5\% difference between the two profiles would
disappear, as the AE solution evolves to be exactly the SE solution -- this
is evident in the asymmetry of the AE PDF near the mode
in Fig. \ref{fig:temp_comparison}b and also
the trend of the mean temperature over time in Fig. \ref{fig:time_trace}c.

One means of comparing two
PDFs to determine if they are drawn from the same underlying
sample distribution is through the use of a Kolmogorov-Smirnov (KS) test \cite{wall&jenkins2012}.
We calculate the KS statistic for a PDF of some value, $q$, as
\begin{equation}
\KS{q} = \text{CDF}_{\text{AE}}(q) - \text{CDF}_{\text{SE}}(q),
\label{eqn:ks_profile}
\end{equation}
where CDF stands for cumulative distribution function, the integral of the PDF.
A traditional Kolmogorov-Smirnov statistic is just a single value,
$\KSstat{q} = |\KS{q}|_\infty =
\text{max} |\KS{q}|$, and we use both the profile KS$(q)$ and
$\KSstat{q}$ to gain insight into the likeness of two PDFs. 
We show the KS profile in Fig. \ref{fig:temp_comparison}d, and the
CDFs used to construct it overlay the PDFs in Fig. \ref{fig:temp_comparison}b.
Near the modes of the temperature PDFs, the $\KSstat{T} = 0.495$, 
which is very large and implies that roughly half of all temperature
measurements in the SE case are greater than those in the AE case.
This difference is significant, and shows that the two PDFs are distinctly different,
but aside from this large value near the modes the KS profile has very small values,
indicating that the temperature fluctuations away from the modes in the two cases are nearly identical.

In addition to comparing the thermodynamic state achieved by the SE and AE methods,
we examine the velocities found in the evolved states.
Shown are the PDFs of 
vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
and the nonlinear vertical convective flux (Fig. \ref{fig:pdf_comparison}c). 
The CDFs of each profile are overplotted, and corresponding KS profiles are
shown in Fig. \ref{fig:pdf_comparison}d-f.  We report
$\KSstat{w} = 0.00615$ (vertical velocity), $\KSstat{u} = 0.0349$ (horizontal velocity),
and $\KSstat{w(T - \angles{T}_{x,y})} = 0.0263$.
Each PDF here shows a strong peak near zero due to the no-slip, impenetrable
velocity boundary conditions (Eqn. (\ref{eqn:bcs})).
The difference in vertical velocity
and heat transport between AE and SE is negligible, which is unsurprising in light of
the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
The horizontal velocity shows some small deviation between the two simulations, and this
likely relates to the nature of the strength of the horizontally oscillatory motions
as we previously described in the context of suppressed Nu scaling. Thus, while
the temperature profiles are distinctly drawn from different distributions in
Fig. \ref{fig:temp_comparison}b, the profiles are similar enough that they drive
nearly identical nonlinear dynamics.

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{Probability distribution functions (PDFs) of (a) the vertical velocity, (b) the horizontal velocity, and (c) nonlinear
convective transport are shown for 2D runs achieved through SE (blue) and AE (red)
at $S = 10^{5}$.  The cumulative distribution function (CDF) is overplotted for each PDF. 
(d-f) The KS statistics, or the values of CDF$_{\text{AE}}$ - CDF$_{\text{SE}}$,
are shown for the related distributions, and solid lines indicated positive values
while dashed lines are negative values. Unlike the temperature distributions in
Fig. \ref{fig:temp_comparison}, these distributions, particularly the vertical
velocity and transport, show very good agreement and small values of the KS statistic.
\label{fig:pdf_comparison} }
\end{figure}

@@

\section{Extensions \& Conclusions}
\label{sec:extensions}
In this work we have studied a method of Accelerated Evolution (AE) which can
be employed to achieve rapid thermal convergence of convective simulations.  We compared
this technique to the Standard Evolution (SE) of convection through a thermal diffusion timescale and
showed that AE rapidly obtains solutions whose dynamics are similar to SE solutions.
The AE method is not only valid at low values of $S$, where SE solutions
converge quickly due to the short thermal timescale, but AE is also applicable
at high values of $S$, where SE solutions are intractable.
As discussed, 2D and 3D are identical short of the time-varying entrainment states
(Fig. \ref{fig:oscillating_plumes}), so we have restricted most of our study to 2D.
However, due to the greater computational expense of 3D runs, they stand to gain more
time savings from AE. This is a sentence about the magnitude of savings involved for
AE vs. SE (wall time + cpu hours, 2d: $10^5$, 3d: $10^4$).

@@

Convection in natural systems is often driven by internal heating processes
rather than imposed, fixed boundary conditions. The AE procedure can be straightforwardly
applied to Boussinesq studies of internally heated convection \cite{goluskin2016},
where a constant source term in the energy equation causes 
the vertical flux through the system to increase with height.
These systems can be
studied using exactly the methods that we examined here, but 
multiplying the flux profiles derived
in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux. Studies of
convection in natural system often employ height-dependent conductivities
\cite{brandenburg2016, kapyla&all2017}, leading
to natural flux divergences that act as internal heating terms.
The study
of AE in the context of simple internal heating simulations will be an important step
towards achieving AE in simulations with astrophysically realistic conductivities.

A further area which could benefit from AE is overshooting convection, in which
studies examine adjacent stable and convecting regions
\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
When the interface between the stable region
and the convecting region is stiff and motions do not cross that interface,
convective motions cannot accelerate the restratification of the stable region.
In fully-convective domains, such as those studied in this work, the thermodynamics evolve
at a more rapid rate than the thermal diffusion time across the domain due to
convective mixing.  For example, in Fig. \ref{fig:time_trace}a,
the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
despite the thermal timescale being roughly $10^4$ freefall units. However, in 
studies where there is a stable region which is not mixed by convection, the experimentalist
must either wait through a thermal diffusion time for the region to restratify
or employ other methods \cite{couston&all2017} to study evolved atmospheres.

Studies of stratified, compressible convection have much to gain through
developing and employing AE.
In many studies of stratified convection, the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}. Thus, the
thermal timescale grows with depth in the atmosphere, and
the difficulty of achieving thermal convergence grows as simulators study more highly
stratified domains.
In order to extend AE into this regime, two additional pieces of information must be considered.
First, rather than constructing the profiles in Eqn. (\ref{eqn:bvp_ratios})
with the total flux through the domain, only the superadiabatic portion of
the flux should be considered.
Second, in addition to solving for
hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously evolve the density
profile in a manner which conserves mass.  In a 1D boundary value problem, such as
is solved to achieve AE here, this implies the inclusion of an equation which tracks
the vertically integrated mass, and sets boundary conditions on that mass to ensure
that no mass enters or leaves the domain. [GIVE NUMBERS]

@@

While the use of a single AE BVP solve rapidly advances the convecting state to
one that is closer to the evolved state, we find that repeating this method 
multiple times is the best way to
ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
set $t_{\text{transient}} = 50$, completed an AE BVP solve
with $t_{\text{min}} = 30$ and $P = 0.1$, and then repeated the procedure.
For all 3D runs and 2D runs with $S \in [10^5, 10^6]$,
we did a first AE BVP solve with $t_{\text{transient}} = 20$,
$t_{\text{min}} = 20$, and $P = 1$ in order to quickly reach a near-
converged state and vastly increase our timestep size.  After this first solve, 
we completed two AE BVP solves, with $t_{\text{transient}} = 30$,
$t_{\text{min}} = 30$, 
and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}c).
At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
$P = 1$. For the first solve, we set $t_{\text{transient}} = 20$, and for the
second we set $t_{\text{transient}} = 30$. We used fewer solves at this high
value of $S$ in part to reduce the computational expense of the run, and in
part because a third BVP generally did not greatly alter the solution
(as in Fig. \ref{fig:time_trace}c, arrow 3). We wait 50 freefall times after
the final AE BVP solve of each run before beginning to take measurements.
